---
title: "Final-Project"
author: "Ryan Corydon and Emma Podlich"
date: "2023-05-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(ggplot2)
```

```{r}
data = read.csv("finalHW.csv")
View(data)

str(data)
```

The data set that we are looking at is the "Superstore Sales Dataset" from Kaggle. This data set contains information about retail sales of a global superstore over 4 years (2011-2014). We plan to analyze this data set in order to find how sales of certain items compare in various countries. This will be useful for finding what the superstore focus their marketing on in each region or "market" based on the results that we find. Since the data set is from Kaggle, the data is fairly clean and easy to read/understand. We plan to further clean the data by creating subdatasets for each "market" to make creating the plots easier. We will also change some of the character variables to factor variables for ease of data processing. 


```{r}
data$ship_date <- as.Date(data$ship_date)
data$order_date <- as.Date(data$order_date)
data$Ship_days <- as.numeric(difftime(data$ship_date, data$order_date, units = "days"))
```

We will use this new variable "Ship_Days" to analyze trends between cost and region to see if they are correlated between the given ship day.


```{r}
dataNew <- data[complete.cases(data),]
str(dataNew)
View(dataNew)
```
An issue with this is that there are some pieces of data that are missing values. We will clean the data removing all of the missing values so we have no issues within the data. This new dataset is much smaller than the original as any row with a null value has been cleaned.


### Shipping Cost By Region

```{r}
dataNew %>% ggplot(aes(shipping_cost)) + geom_boxplot(aes(colour = region)) + facet_wrap(~region) + ggtitle("Shipping Cost By Region Boxplot") + labs(x = "Shipping Cost (dollars)")
```

We expected to see the highest shipping costs for the most rural regions such as Africa and Asia. The box plot of shipping cost by region above indicates that we were somewhat correct with our prediction. There are the most outliers of high shipping costs in the Central, South, and West regions. However, it is difficult to see the exact means of shipping cost by region as there are lots of outliers in each region. Therefore, to see more exact comparisons, we did further data processing seen below.

```{r}
shipping = dataNew %>% select(region, shipping_cost)
shipping$region <- as.factor(shipping$region)
shippingsummary = shipping %>% group_by(region) %>%
  summarise(shipping_cost = mean(shipping_cost))

shippingsummary
```

In order to get the average shipping cost by region, we did a couple steps of data processing. We selected the region and shipping cost variables into a new dataframe. Then, made the region as a factor variable and grouped by region to summarise the mean shipping cost by region.

```{r}
shippingsummary %>% mutate(region = reorder(factor(region), shipping_cost, mean, na.rm=TRUE)) %>% ggplot(aes(x = region, y = shipping_cost)) + geom_bar(stat = 'identity') + ggtitle("Average Shipping Cost By Region Bar Chart") + labs(y = "Average Shipping Cost (dollars)", x = "Region")
```

We expected to see the highest shipping costs for the most rural regions such as Africa and Asia. The bar plot of average shipping cost by region above indicates that we were somewhat correct with our prediction. The highest average shipping costs are in regions in Asia, however, Africa's average shipping costs are fairly low which was surprising. This company could work on reducing shipping costs in Asia to help expand their market in Asia. They could also advertise low shipping costs in Afria to help appeal towards the market in Africa.


### Profit by Year and Region

```{r}
dataNew$profit <- as.numeric(dataNew$profit)

profits = dataNew %>% group_by(year, region) %>% summarise(total_profit = sum(profit))
profits

profits %>% ggplot(aes(x = year, y = total_profit, colour = region)) + geom_line() + facet_wrap(~region) + ggtitle("Total Profit by Year and Region") + labs(x = "Year", y = "Total Profit (dollars)")
```
To clean the data for creating a profit chart by year and region, the first step was making profit a numeric variable from its previous character type. Then, a new dataframe was created that indicated the sum of profits in each region and year that was plotted into a line plot. 

We expected that profits would increase over time for the most part as the years increased. We also believed that the profits would be highest in the western and central regions. According to the line plot, our predictions were not completely correct. In most regions, total profits increased until 2014 when there was a little bit of a decrease. However, profits were the highest in all four years in the central region. If the company would like to expand their marker, then they should focus advertising in the regions with less profits such as Oceania, Southern Asia, and Canada where their profits are low. If the company would like to focus on increasing profits in the best profitable regions, then they should focus advertising in the regions with higher profits such as Central, North, and Northern Asia.



### Ship Days by Order Priority 

```{r}

```



### Sales by Category

There are three categories of items that can be bought, office supplies, technology, and furniture. We want to analyze the amount of profits per each category and segment to see where the company makes the most money.
```{r}

totalSales = dataNew %>% group_by(category,segment) %>% summarise(total_profit = sum(profit))
totalSales
ggplot(totalSales, aes(x = category, y = total_profit, fill = segment)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Total Profit by Segment and Category",
       x = "Category",
       y = "Total Profit",
       fill = "Segment")
```
It can be seen that orders from this company are mainly from consumers as they are purchasing the most furniture, office supplies, and technology. While Home offices are spent the least on every category as well. Most of these orders are spent on technology with a maximum profit of 96,189.28 dollars. As well the least spent was home office furniture at 16,599.82 dollars. 
