---
title: "Final-Project"
author: "Ryan Corydon and Emma Podlich"
date: "2023-05-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

```{r}
data = read.csv("finalHW.csv")
View(data)

str(data)
```

The data set that we are looking at is the "Superstore Sales Dataset" from Kaggle. This data set contains information about retail sales of a global superstore over 4 years (2011-2014). We plan to analyze this data set in order to find how sales of certain items compare in various countries. This will be useful for finding what the superstore focus their marketing on in each region or "market" based on the results that we find. Since the data set is from Kaggle, the data is fairly clean and easy to read/understand. We plan to further clean the data by creating subdatasets for each "market" to make creating the plots easier. We will also change some of the character variables to factor variables for ease of data processing. 


```{r}
data$ship_date <- as.Date(data$ship_date)
data$order_date <- as.Date(data$order_date)
data$Ship_days <- as.numeric(difftime(data$ship_date, data$order_date, units = "days"))
```

We will use this new variable "Ship_Days" to analyze trends between cost and region to see if they are correlated between the given ship day.


```{r}
dataNew <- data[complete.cases(data),]
str(dataNew)
View(dataNew)
```
An issue with this is that there are some pieces of data that are missing values. We will clean the data removing all of the missing values so we have no issues within the data. This new dataset is much smaller than the original as any row with a null value has been cleaned.

